% !TEX root = ../manuscript.tex

\section{Results}

\subsection{Geologic Controls on PREDICT Fault Properties}

\todo{Report matched-effect estimates for sand proportion, thickness
uniformity, faulting depth, clay volume fraction in sand, and clay volume
fraction in clay. Separate directional effects on $k_{xx}$, $k_{yy}$, and
$k_{zz}$ and connect them to the fault-material and tensor-rotation mechanisms
in PREDICT.}

\subsection{Hierarchical Reduction and Three-Dimensional Fault Cases}

\todo{Summarize cluster-count frequencies, state-library composition, window
similarity-group structures, pairwise co-grouping frequencies, and their
dependence on geology. Show how independent, fault-wide low/high, and grouped
low/high designs translate into $6\times87$ fault-property fields. Emphasize
that the reduction retains actual joint realizations and important multimodal
behavior.}

\subsection{Upscaled Multiphase Fault Properties}

\todo{Present spatial variation in porosity, capillary-pressure entry levels,
effective irreducible water saturation, and relative permeability. Compare the
full slice-level and entry-pressure-branch representations and document the
final choice used in the reservoir ensemble.}

\subsection{Field-Scale \coTwo{} Migration and Containment}

\todo{Report storage-reservoir retention, entry into the fault and top seal,
maximum upward migration, and dissolved-versus-free phase partitioning over
the injection and post-injection periods. Lead with the principal physical and
decision-relevant findings rather than intermediate workflow diagnostics.}

\subsection{Contributions of the Uncertainty Hierarchy}

\todo{Quantify how much outcome variability is associated with geology,
within-window PREDICT stochasticity, and cross-window coupling assumptions.
Identify interactions and the conditions responsible for the most secure and
least secure migration outcomes.}
